Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-20 writeup/rocha_etal.tex
Small fix

%
%
%\begin{figure*}[ht]
%  \begin{center}
%    \includegraphics[width=.65\textwidth]{figs/fig5.pdf}
% \caption{\small Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
% in the 1/48$^\circ$ simulation. Solid lines
% are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
% fields.}
% \label{fig5}
% \end{center}
%\end{figure*}
%
%
%Figure \ref{fig5}a depicts the horizontal wavenumber spectra of surface KE in
%April and October. At scales larger than 20 km, the April and October spectra based on hourly
%velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
%Consistent with the results of
%\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
%there is significant high-frequency variabilty at submesoscales. Daily-averaging
%the velocity field suppresses spatial variability at scales smaller than about 250
%km, both in April and October (compare solid lines against dashed lines in Figure
%\ref{fig5}a). But this suppression is dramatic in October, when the IGWs peak. At scales
%smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
%flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
%is strong, consistent
%with the results of \citet{sasaki_etal2014}, which are
%based on daily-averaged velocity fields of a different model without tidal forcing
%(P. Klein, personal communication).
%
%The IGWs project on the sea-surface.
%There is a dramatic difference between the spectra
%based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig5}b): at scales smaller than 100 km, the spectra
%of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
%sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
%flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
%turbulence and near-surface submesoscale IGWs conspire to yield weak seasonality
%in the spectra of KE and sea-surface height variance based on hourly fields.
%
%
\section{Discussion and conclusion}
Our work adds to recent modeling \citep[e.g., ][]{sasaki_etal2014}
and observational \citep[e.g., ][]{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale IGWs in the Kuroshio Extension undergo
a strong seasonal cycle that is out of phase with the seasonal cycle of
submesoscale turbulence. IGW energy and SSH variance are significantly spread across
the submesoscales, likely through mesoscale refraction and dispersion \citep[e.g.,][and references therein]{ponte_klein2015,alford_etal2016}
 and parametric
sub-harmonic instability \citep[e.g., ][]{mackinnon_winters2005}. In the LLC simultions,
super-inertial IGWs account for most of the surface submesoscale KE and SSH variance;
near-inertial IGWs project onto larger scales.

@@

Internal tide energy flux does not show a seasonal modulation \citep[e.g.,][]{alford2003},
hence one expects a strong seasonality in the near-surface
expression of internal tides and
higher frequency IGWs if the near-surface stratification varies strongly.
Windy near-inertial wave (NIW) generation is bursty and peaks in early winter, but
NIW energy appears to have similar energy level in October and April
\citep{alford_etal2016}.
While NIWs are generated at large scales, mesoscale turbulence can
refract and disperse those waves in few inertial periods, thereby generating
submesoscale (10-100 km) near-inertial waves \citep[][and references therein]{alford_etal2016}.
But in our simulations the higher frequency inertia-gravity-wave
account for most of the seasonality in super-inertial surface KE and SSH
(Figure \ref{fig4}a-b), possibly because submesoscale
NIWs quickly propagate into the interior and weakly project onto SSH.

>>>>

%
%
%\begin{figure*}[ht]
%  \begin{center}
%    \includegraphics[width=.65\textwidth]{figs/fig5.pdf}
% \caption{\small Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
% in the 1/48$^\circ$ simulation. Solid lines
% are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
% fields.}
% \label{fig5}
% \end{center}
%\end{figure*}
%
%
%Figure \ref{fig5}a depicts the horizontal wavenumber spectra of surface KE in
%April and October. At scales larger than 20 km, the April and October spectra based on hourly
%velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
%Consistent with the results of
%\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
%there is significant high-frequency variabilty at submesoscales. Daily-averaging
%the velocity field suppresses spatial variability at scales smaller than about 250
%km, both in April and October (compare solid lines against dashed lines in Figure
%\ref{fig5}a). But this suppression is dramatic in October, when the IGWs peak. At scales
%smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
%flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
%is strong, consistent
%with the results of \citet{sasaki_etal2014}, which are
%based on daily-averaged velocity fields of a different model without tidal forcing
%(P. Klein, personal communication).
%
%The IGWs project on the sea-surface.
%There is a dramatic difference between the spectra
%based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig5}b): at scales smaller than 100 km, the spectra
%of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
%sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
%flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
%turbulence and near-surface submesoscale IGWs conspire to yield weak seasonality
%in the spectra of KE and sea-surface height variance based on hourly fields.
%
%
\section{Discussion and conclusion}
Our work adds to recent modeling \citep[e.g., ][]{sasaki_etal2014}
and observational \citep[e.g., ][]{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale IGWs in the Kuroshio Extension undergo
a strong seasonal cycle that is out of phase with the seasonal cycle of
submesoscale turbulence. IGW energy and SSH variance are significantly spread across
the submesoscales, likely through mesoscale refraction and dispersion \citep[e.g.,][and references therein]{ponte_klein2015,alford_etal2016}
 and parametric
sub-harmonic instability \citep[e.g., ][]{mackinnon_winters2005}.
In the LLC simultions,
super-inertial IGWs account for most of the surface submesoscale KE and SSH variance;
near-inertial IGWs project onto larger scales, possibly because submesoscale
NIWs quickly propagate into the interior and weakly project onto SSH.

@@

Internal tide energy flux does not show a seasonal modulation \citep[e.g.,][]{alford2003},
hence one expects a strong seasonality in the near-surface
expression of internal tides and
higher frequency IGWs if the near-surface stratification varies strongly.
Windy near-inertial wave (NIW) generation is bursty and peaks in early winter and
NIW energy is similar energy level in October and April
\citep{alford_etal2016}, but in our simulations the higher frequency inertia-gravity-wave
account for most of the seasonality in super-inertial surface KE and SSH
(Figure \ref{fig4}a-b),
